wgcna

### 2019-08-23 analysis/08_wgcna.Rmd
intro

This first image was made using [`08_WGCNA_1.R`](https://github.com/macmanes-lab/DoveParentsRNAseq/blob/master/analysis/08_WGCNA_1.R), which was modified from the [first in a series of WGCNA tutorial](https://horvath.genetics.ucla.edu/html/CoexpressionNetwork/Rpackages/WGCNA/Tutorials/Consensus-DataInput.R). The first tutorial focuses on data input, cleaning and pre-processing; outlier removal; clustering of samples by their Euclidean distance; a comparison of sample cluster to sample meta data.

>>>>

# WGCNA analysis, first pass

The anlayses and image was made by following along with and modifing the [first in a series of WGCNA tutorial](https://horvath.genetics.ucla.edu/html/CoexpressionNetwork/Rpackages/WGCNA/Tutorials/Consensus-DataInput.R). The first tutorial focuses on data input, cleaning and pre-processing; outlier removal; clustering of samples by their Euclidean distance; a comparison of sample cluster to sample meta data. I put pretty much the whole script into a single function that I source with [`08_WGCNA_1.R`](https://github.com/macmanes-lab/DoveParentsRNAseq/blob/master/analysis/08_WGCNA_1.R).
